\documentclass{resume}

\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support 

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\name{JIE NIU}

% (\kaishu{牛偈})

\basicInfo{
  \email{jie.niu@queensu.ca} \textperiodcentered\ 
  \phone{613-583-2147} \textperiodcentered\ 
  \linkedin[jieniu]{https://www.linkedin.com/in/jieniu} \textperiodcentered\ 
  \github[qu-jieniu]{https://github.com/qu-jieniu}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Queen's University at Kingston}}{2017 -- 2022}
\textit{Bachelor of Computing (Hon.)} specialize in Computer Science and Mathematics

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\faUniversity\ Academia Experience}

\datedsubsection{\textbf{Adjunct Instructor}}{Jan. 2023 -- Apr. 2023}
\companyName{{St. Lawrence College}, Kingston, ON} {}
COMP 53 -- Intermediate Database
\begin{itemize}
  \item Taught beginning to intermediate SQL concepts for database design and querying;
  \item Facilitated class discussions in-person and via online hybrid;
  \item Introduced students to advanced database topics.
\end{itemize} 

\datedsubsection{\textbf{Research Assistant}}{Jan. 2022 -- Present}
\companyName{{Smith School of Business}, Queen's University} {}
Delivered technical components to support research projects.   

\vspace{0.5em}
\hspace{0.7em}\emph{Past and Current Projects}:
\begin{itemize}

  \item \datedline{Conducted geospatial analysis to map 3G mobile coverage across U.S. Census ZIP Code Tabulation Areas \mbox{(ZCTAs)} using shapefiles and data in GeoTIFF format. }{}
    \subitem Tools used: R, ArcGIS
    \subitem Supervisor: \emph{Prof.} Shu Zhang \& Yu Hou

  \item \datedline{Data Mining on Bloomberg Terminal combined with financial databases (WRDS). 
  Wrote automated scripts to extract current corporate credit ratings and update in database. }{} 
      \subitem Tools used: R, PostgreSQL, GitHub CI/CD Actions
      \subitem Supervisor: \emph{Prof.} Evan Jo

  \item \datedline{Research data processing on retirement, longevity, and annuity pricing. 
  Virtual file system implementation for database file storage.}{}
      \subitem Tools used: R, PostgreSQL, Linux HPC
      \subitem Supervisor: \emph{Prof.} Evan Jo

  \item \datedline{Web scraping for financial data from Yahoo Finance. 
  Built time series data and conducted sentiment analysis on user conversations.}{}
      \subitem Tools used: Python, R, Docker
      \subitem Supervisor: \emph{Prof.} Jingyu Zhang

\end{itemize}

\datedsubsection{\textbf{Teaching Assistant}}{Jan. 2022 -- Present}
\companyName{{Smith School of Business}, Queen's University} {}
\vspace{-.5em}

\begin{itemize}
  \item \datedline{COMM 121 (Introduction to Finance, Fall 2024)}{}
  {Head TA - managed course logistics , facilitied exams \& accommodations, maintained student records.}\\
  {Supervisor: \emph{Prof.} Alison Taylor \& Evan Jo}\\
  \vspace{-0.5em}
  
  \item \datedline{COMM 420 (Financial Technology and Innovation, 2022/23/24)}{}
  {Graded assignments; facilitated R programming workshops for quantitative trading. }\\
  {Supervisor: \emph{Prof.} Evan Jo}\\
  \vspace{-0.5em}
  
  \item \datedline{MGMT 921 (Capital Markets, Theory and Empirics, 2022/23/24)}{}
  {Conducted workshops and tutorials on R, Python, PostgreSQL, and WRDS.}\\
  {Supervisor: \emph{Prof.} Evan Jo}\\
  \vspace{-0.5em}
  
  \item \datedline{COMM 493 (Analytics \& AI for Business, Winter 2023)}{}
  {Graded business case and coding assignments; developed technical documentation for students.}\\
  {Supervisor: \emph{Prof.} Shaun Cahill}\\
  \vspace{-0.5em}
    
  \item \datedline{COMM 161 (Intro. to Mathematical Analysis, Fall 2022)}{}
  {Head TA - supervised grading, organized weekly tutorials, maintained student records.}\\
  {Supervisor: \emph{Prof.} Matthew Thompson}\\
  \vspace{-0.5em}
  
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\faBriefcase\ Professional Experience}

\datedsubsection{\textbf{Administrative Assistant}}{Apr. 2021 -- Present}
\companyName{{Smith School of Business}, Queen's University} {}
Supported faculty members, utilized PeopleSoft, managed course websites through D2L, prepared expense claims, organized supplies, and performed other essential tasks as needed. 

\datedsubsection{\textbf{Technical Support Representitive}}{Jan. 2021 -- Apr. 2021}
\companyName{{Kingston Online Services}, Kingston, ON} {}
Assisted customers by troubleshooting internet connection and email issues, configured hardware, and responded to calls and support tickets in a help desk.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\faUser\ Personal Projects}
\begin{itemize}[parsep=0.5ex]
  \item LinkedIn data harvesting
  \item SEC EDGAR archiving and analysis
  \item Studying for RHCSA linux certification 
  \item Frontend and backend design of a homomorphic encryption algorithm
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Writing: \LaTeX
  \item Programming Languages: R == SQL > Python == C > Java
  \item Platform: Mac; Linux; HPC Clusters (\emph{High Performance Computing}) 
  \item Development: Containers (Docker, Podman, Singularity), Web Development (Django, Flask, R Shiny)
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\faHeartO\ Honors and Awards}
\datedline{Queen's University Excellence Scholarship}{Sep. 2017}
\datedline{Queen's University General Bursary}{Apr. 2020}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item Notable undergraduate courses:
      \textit{Logic for Computer Science, Calculus III, Graph Theory}
  \item Languages: English (Professional), Mandarin (Native)
  \item Citizenship: Chinese
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\phantom{}\blfootnote{Updated in October 2024}
\end{document}
